---
title: "CUNY DATA 609 HW4"
author: "Raphael Nash"
date: "9/11/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("ggplot2")
```


#P191 # 3
Using Monte Carlo simulation, write an algorithm to calculate an approximation to $\pi$ by considering the number of random points selected inside the quarter x  circle:

$$Q: x^2 + y^2 = 1, x \ge 0 , y \ge 0 $$
where the quarter circle is taken to be inside the square:

$$S: 0 \le x \le 1 \enspace and \enspace  0 \le y \le 1 $$
```{r}

points_df <- data.frame (x=runif(100000), y= runif(100000) ) 

points_df$in_out <- NA

points_df$in_out <- ifelse(points_df$x^2 + points_df$y^2 < 1 , "inside" , "outside")

points_df$in_out <- factor(points_df$in_out)

ggplot(points_df, aes( x= x, y=y, colour = in_out )) + geom_point() 

```


My estimate of $\pi$ is: `r (nrow(subset(points_df, in_out == "inside") )  / nrow(points_df )) * 4 ` 


#p194 # 1 



 

```{r}

mid_sq <- function(seed, n) {
  if (nchar( toString(seed))  < 4)  {
    print ( "enter an at least4 digit #") 
    return()
  }
  
  v <-  vector()
  
  
  for ( i in 1:n) {
    
    seed <- seed^2 
    
    seed_str <- toString(seed) 
    
    while (nchar( seed_str ) < 8 )  {
      seed_str <- paste("0", seed_str, sep  = "")
      
    }
    
    seed <- as.numeric ( substring ( seed_str,2,6))
    v <- c(v,seed)
  }
  v
  
}



```

Use the middle-square method to generate:  
a. 10 random numbers using $x_0 = 1009$ . 

```{r}
mid_sq( 1009, 10)
```

b. 20 random numbers using $x_0 = 653217$ . 
```{r}
mid_sq( 653217, 20)
```

c. 15 random numbers using $x_0 = 3043$ . 
```{r}
mid_sq( 3043, 15)
```
 

d. Comment about the results of each sequence. Was there cycling? Did each sequence degenerate rapidly?
No I did not experience cycling.  The number generated ran very fast.

#p211 #2 

In many situations, the time T between deliveries and the order quantity Q is not xed. Instead, an order is placed for a speci c amount of gasoline. Depending on how many orders are placed in a given time interval, the time to ll an order varies. You have no reason to believe that the performance of the delivery operation will change. Therefore,you have examined records for the past 100 deliveries and found the following lag times, or extra days, required to ll your order:

```{r}

delivery_df <- data.frame(
   T = c(2,3,4,5,6,7),
   num = c(10,25,30,20,13,2)
)

```

Construct a Monte Carlo simulation for the lag time submodel. If you have a handheld calculator or computer available, test your submodel by running 1000 trials and comparing the number of occurrences of the various lag times with the historical data.

```{r}

delivery_df$observed_prob <- delivery_df$num / sum(delivery_df$num) 
delivery_df$cum_prob <- cumsum(delivery_df$observed_prob)


ggplot(delivery_df, aes(y= T,x = cum_prob)) + geom_point() 

```


This is the monte carlo simulation:  
```{r}

# the variables prev_prob and this_prob create the interval of cumulative probabilit to look in for the results.   

sim_results <- vector()

pos <-0

for (i in runif(1000, min = 0 , max = 1 ))  {
  prev_prob <- 0 
  

  for ( x in 1: NROW(delivery_df)){
    this_prob <- delivery_df[x,"cum_prob"]  
    if ( (i >= prev_prob) && (i <= this_prob )   ) {
      sim_results <- c( sim_results, delivery_df[x,"T"]  )
      break
    }
    prev_prob <- this_prob
    
  }
      

}

```






```{r}


sim_results <-    table(unlist(sim_results))
sim_results <- as.data.frame(sim_results)

 
sim_results$predicted_prob <- sim_results$Freq / sum(sim_results$Freq) 
colnames (sim_results) <- c("T", "predicted_freq", "predicted_prob")

delivery_df <- merge(delivery_df, sim_results)
delivery_df

```


Monte Carlo results.... 

Observed_prob is from the problem and predicted_prob is the results of the simulation.    
```{r}

delivery_df[c("T", "predicted_prob", "observed_prob")]
```


